Variants of G\"{o}del's Ontological Proof \\ in a Natural Deduction Calculus

### 2016-06-14 Papers/InProgress/NaturalDeduction/GodProof-ND.tex
Revert "conclusion section"
This reverts commit 97ce5bd05b1cd541a4fbbb8b14bded7627d879d0.

The proof of section \ref{sec:newproof} shows explicitly that the weak modal system {\bf KB} is sufficient for the ontological argument as opposed to the standard modal calculus {\bf S5}. This weakening of the system is based on an explicit formalization and confirms the result briefly described by Anderson \citep[footnote 2]{and90}. The weakening also applies to the emendation and variant of Anderson and Bj\o rdal respectively. The proofs are short and accessible to the general reader because of the choice of a natural deduction calculus. In addition to weakening the modal system the proof of section \ref{sec:newproof} shows that the equality relation is not needed to prove the main theorem. In the second proof of section \ref{sec:anderson} the axioms 4 and 5 as well as definitions 2 and 3 are explicitly shown to be redundant in Anderson's emendation.

>>>>

The proof of section \ref{sec:newproof} shows explicitly that the weak modal system {\bf KB} is sufficient for the ontological argument as opposed to the standard modal calculus {\bf S5}. This weakening of the system is based on an explicit formalization and confirms the result briefly described by Anderson \citep[footnote 2]{and90}. The weakening also applies to the emendation and variant of Anderson and Bj\o rdal respectively. The proofs are short and accessible to the general reader because of the choice of a natural deduction calculus.
